Simulations to test ctwas summary stats version, 45k samples, a few new setings required

### 2023-06-10 analysis/index.Rmd
low PVE simulation bug fix
more settings for low SNP PVE

* [**Using UKbiobank data (113k samples), fusion weights Adipose, more settings with low SNP PVE **](simulation-ctwas-ukbWG-gtex.adipose_s200.113_03212023.html)

>>>>

* [**Using UKbiobank data (110k samples), fusion weights Adipose, more settings with low SNP PVE **](simulation-ctwas-ukbWG-gtex.adipose_s200.113_03221023.html)

### 2023-06-10 analysis/simulation-ctwas-ukbWG-gtex.adipose_s200.113_03212023.Rmd
more settings for low SNP PVE

```{r config-1, fig.height=3, fig.width=8, message=F, eval=F}

@@

simutags <- paste(1, c(1:24, 26:54, 56:70), sep = "-")
# configtag <- 1
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
#plot_fusion_coloc(configtag, runtag, simutags)
# plot_focus(configtag, runtag, simutags)
#print("FOCUS result is null")
#plot_smr(configtag, runtag, simutags)

>>>>

```{r config-1-2, fig.height=3, fig.width=8, message=F}

@@

# has not rerun last step for simu 1-x. 
# simutags <- paste(1, c(1:24, 26:54, 56:70), sep = "-")
# configtag <- 1 
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# plot_par(1, runtag, simutags)
# print("When running with L= 5 in final step:")
# plot_PIP(1, runtag, simutags)
# print("When running with L= 1 in final step:")
# plot_PIP(2, runtag, simutags)
#plot_fusion_coloc(configtag, runtag, simutags)
# plot_focus(configtag, runtag, simutags)
#print("FOCUS result is null")
#plot_smr(configtag, runtag, simutags)

### 2023-06-10 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_03222023.Rmd
more settings for low SNP PVE

# simutags <- paste(1, c(1:5), sep = "-")
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# # plot_fusion_coloc(configtag, runtag, simutags)
# # # plot_focus(configtag, runtag, simutags)
# # print("FOCUS result is null")
# # plot_smr(configtag, runtag, simutags)
# 
# simutags <- paste(2, 1:5, sep = "-")
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# # plot_fusion_coloc(configtag, runtag, simutags)
# # #plot_focus(configtag, runtag, simutags)
# # plot_smr(configtag, runtag, simutags)
# 
# simutags <- paste(3, 1:5, sep = "-")
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# # plot_fusion_coloc(configtag, runtag, simutags)
# # #plot_focus(configtag, runtag, simutags)
# # plot_smr(configtag, runtag, simutags)
# 
# simutags <- paste(4, 1:5, sep = "-")
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# # plot_fusion_coloc(configtag, runtag, simutags)
# # #plot_focus(configtag, runtag, simutags)
# # plot_smr(configtag, runtag, simutags)
# 
# simutags <- paste(5, c(1:5), sep = "-")
# plot_par(configtag, runtag, simutags)
# plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

>>>>

simutags <- paste(1, c(1:5), sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)

# plot_fusion_coloc(configtag, runtag, simutags)
# # plot_focus(configtag, runtag, simutags)
# print("FOCUS result is null")
# plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(5, c(1:5), sep = "-")
plot_par(1, runtag, simutags)
print("When running with L= 5 in final step:")
plot_PIP(1, runtag, simutags)
print("When running with L= 1 in final step:")
plot_PIP(2, runtag, simutags)
